---
title: "Predict Case-Shiller Home Price Index (Chicago)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Motivation
**Question** Can we use a real-time selected sample to predict the overall market trend?  
Redfin data center provides monthly real estate information of houses listed on their website.  The data are updated each month.  On the other hand, Case-Shiller Home Price Index measures the value of the residential real estate and is reported with two month lag.  Redfin data are an almost real-time selected sample while case-Shiller Home Price Index is a general survey with lags.

```{r, echo = F}
rm(list = ls())
redfin <- read.csv("~/working_datasets/redfin/data_crosstab-chicago-asof-201812.csv", fileEncoding = "UCS-2LE", sep = "\t")
```
# Data Preprocessing
This exercise uses Case-Shiller Home Price Index of Chicago downloaded from FRED database using _quantmod_ package and Redfin single-family home listing data download from [Redfin Data Center](https://www.redfin.com/blog/data-center).

```{r data}
# data preprocessing
require(quantmod)
require(zoo)
# download case-shiller housing price index Chicago seasonally adjusted
getSymbols('CHXRSA', src='FRED')
# ================================
# load redfin data
rfDf <- subset(redfin, Region == "Chicago, IL", select = c("Month.of.Period.End", "Median.Sale.Price", "Homes.Sold", "New.Listings", "Inventory", "Days.on.Market", "Average.Sale.To.List"))

rfDf$Month.of.Period.End <- as.yearmon(rfDf$Month.of.Period.End)
# process strings into numbers
rfDf$New.Listings <- as.numeric(gsub(",", "", rfDf$New.Listings))
rfDf$Inventory <- as.numeric(gsub(",", "", rfDf$Inventory))
rfDf$Median.Sale.Price <- as.numeric(gsub("\\D", "", rfDf$Median.Sale.Price)) * 1000
rfDf$Average.Sale.To.List <- as.numeric(gsub("\\D", "", rfDf$Average.Sale.To.List)) * 0.001
```

```{r eda_plot}
require(ggplot2)
df <- as.data.frame(CHXRSA)
df$mon <- as.yearmon(row.names(df))

pltDf <- merge(df, rfDf, by.x = "mon", by.y = "Month.of.Period.End")

p1 <- ggplot(pltDf, aes(x = mon, y = Median.Sale.Price/1000)) + geom_bar(stat = "identity", fill = "#00a0dc") + expand_limits(y = 0) + scale_x_yearmon(breaks =  scales::pretty_breaks(n = 4)) + xlab("") + ylab("Median Sale Price ($K)") + theme(
  panel.background = element_blank(),
  panel.grid.major.y = element_line(colour = "grey80"),
  panel.border = element_rect(colour = "grey80", fill = NA)
) + ggtitle("RedFin Single-Family Housing Sale Price")
print(p1)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
